---
title: "Intro to R"
output: html_notebook
---

```{r setup, include=FALSE, echo=FALSE}
require("knitr")
opts_knit$set(root.dir = "~/Desktop/af-werx/data")
```

# Setting directory
```{r}
setwd("~/Desktop/af-werx")
```

# Getting working directory
```{r}
getwd()
```

# Set our dirs
```{r}
main_dir = "~/Desktop/af-werx"
data_dir = paste0(main_dir, "/data")
plot_dir = paste0(main_dir, "/plots")
setwd(data_dir)
getwd()
```

# Read CSV
```{r}
temp_heart_rate = read.csv("temp_heart_rate.csv", header = T, stringsAsFactors = F)
```

# Structure of the Data
```{r}
str(temp_heart_rate)
```


# View the first rows of the Data
```{r}
head(temp_heart_rate)
```

# View the last rows of the data
```{r}
tail(temp_heart_rate)
```


# View the whole data
```{r}
View(temp_heart_rate)
```

# Writing data
```{r}
temp_heart_subset = temp_heart_rate[1:10,]
write.csv(temp_heart_subset, "temp_heart_subset.csv", row.names = F)
```

# View objects that are in environment
```{r}
ls()
```

# Save environment
```{r}
save.image(file = "myenv.RData")
```


# Remove variable
```{r}
rm("temp_heart_rate")
ls()
```

# Remove whole environment
```{r}
# if you don't want to use the broom
rm(list=ls())
```

# Loading the Environment
```{r}
load("myenv.RData")
```

# CMP
```{r}
CMP = read.csv("ChemicalManufacturingProcess.csv", header=T, stringsAsFactors = F)
str(CMP)
```


# View CMP Data
```{r}
View(CMP)
```

```{r}
column_ids = c(1:4, 14:16)
column_ids
```

# Create CMP Subset with the column_ids vector
```{r}
CMP_subset = CMP[,column_ids]
str(CMP_subset)
```

```{r}
summary(CMP_subset)

```

# Getting Max
# ignore NA in column with na.rm=T
```{r}
maxprocess01 = max(CMP_subset$ManufacturingProcess01, na.rm = T)
maxprocess01
```

# Check NAs is Manufacturing Process 01
```{r}
is_na = is.na(CMP_subset$ManufacturingProcess01)
```

```{r}
View(CMP_subset)
```

# which
```{r}
which(is_na)
```









